Test Suite Parallelization in Open-Source Projects:\\ A Study on Its Usage and Impact

### 2019-05-20 tse19/main.tex
Added Comment

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure.

@@

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of August 25th 2017, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects.

>>>>

We used \github{}'s search API~\cite{githubsearch} to identify
projects that satisfy the following criteria: (1) the primary language
is Java\footnote{In case of projects in multiple languages, the
  \github{} API considers the predominant language as the primary
  language.}, (2) the project has at least 100 stars, (3) the latest
update was on or after January 1st, 2016, and (4) the \emph{readme}
file contains the string \emph{mvn}.  We focused on Java for its
popularity.  Although there is no clearcut limit on the number of
\github{} stars~\cite{github-stars} to define relevant projects, we
observed that one hundred stars was enough to eliminate trivial subjects. The
third
criteria serves to skip projects without recent activity. The fourth
criteria is an approximation to find Maven projects.\Comment{ The
  rationale is that if the string \emph{mvn} exists in the
  \emph{readme} file, it may represent a Maven call (\eg, to compile
or to test the project).} We focused on Maven for its popularity on
Java projects.  Important to highlight that, as of now, the
\github{}'s search API can only reflect contents from repository
statistics (\eg, number of forks, main programming language); it does
not provide a feature to search for projects containing certain files
(\eg{}, \emph{pom.xml}) in the directory structure. 
\textcolor{red}{[S.J: Hoje em dia ja e possivel buscar projeto que contenha determinado arquivo pelo Github API (ex.: pom.xml), SearchCode, foi utilizado PyGithub para filtrar os projetos ]}

@@

We used the following methodology to select projects for analysis. After obtaining the list of potential projects from GitHub, we
filtered those
containing a \pomf{} file in the root directory.\Comment{  A Maven project may
contain several sub-modules with multiple \pomf{} files.}
Then, considering this set of Maven projects, we
executed the tests for \SubjectsReruns{} times to discard those projects with
issues
in the build file and non-deterministic results observed from sequential
executions.
As of August 25th 2017, our search criteria returned a total of
\SubjectsGithub{}
subjects.
From this set of projects,
\SubjectsGithubNotMaven{} projects were not Maven or did not have a
\pomf{} in the root directory, 
\SubjectsGithubNotTestable{} projects were not considered because of
environment incompatibility
(\eg, missing\Comment{ required web browser or database management
system}~DBMS),
\SubjectsGithubFlaky{} projects were discarded because of
``flaky tests''~\cite{luo-etal-fse2014}. A ``flaky'' test is a test that passes
or fails under
the same circumstances leading to non-deterministic results.
As some of our experiments consist of running tests on different
threads, we ignored these projects as it would be impractical
to identify whether a test failed due to a race condition or some
other source of flakiness.
From the remaining \SubjectsGithubConsistant{} projects with
deterministic results, we eliminated \SubjectsGithubTooManyFailures{}
projects with \SuiteFailingThreshold{} or more failing tests as to
reduce bias. For the
remaining projects with failing tests, we used the JUnit's
\CodeIn{@Ignore} annotation to ignore failing tests.
Our final set of subjects contains \numSubjs{} projects. 
 \textcolor{red}{[S.J: Utilizando o script desse experimento, Foram encontrado um total de 4111, onde 3154 nao eram Maven e 957 eram Maven. Dos 3154 que nao eram Maven, 2302 eram Gradle (73\%) ]}
